### 2023-12-26 sections/4-results.tex
added indexing time plots

% These are going to be boring; saving the interesting discussion for the discussion section

@@

>>>>

@@

\subsection{Indexing and Tuning Time}
\label{subsec:indexing-time-results}

For each of the ANN benchmark datasets and the Random dataset, we report the time taken for each algorithm to build the index and to tune the hyperparameters for these indices to achieve the highest possible recall.

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{plots/fashion-mnist-indexing.png}\\
    \subcaption{Fashion-mnist}
    \label{fig:results:fashion-mnist-indexing}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{plots/glove-25-indexing.png}\\
    \subcaption{Glove-25}
    \label{fig:results:glove-25-indexing}
    \end{subfigure}
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{plots/sift-indexing.png}\\
    \subcaption{Sift}
    \label{fig:results:sift-indexing}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{plots/random-indexing.png}\\
    \subcaption{Random}
    \label{fig:results:random-indexing}
    \end{subfigure}%
    \\
    \vspace{1em}
    \caption{Indexing and tuning time with each of the ANN benchmark datasets and the Random dataset.}
    \label{fig:results:indexing}
\end{figure}
